# Exercise 2

The created data (*learning2014.csv*) is read into a variable and necessary libraries are loaded (*ggplot2* and *GGally* for creating plots).

```{r}
library(ggplot2)
library(GGally)
learning_survey_data <- read.csv("./data/learning2014.csv", header = TRUE)
```

## Description of the data

The data under scrutiny is derived from a student survey about approaches to learning.
Original data consists of 183 participants.
However, for this analysis, those with no exam points were omitted, leaving the total number to 166.

```{r}
dim(learning_survey_data)
str(learning_survey_data)
```

The analysis variables are as follows:

* **Gender**
* **Age**
* **Attitude**: Attitude towards learning statistics.
* **Deep**: deep approach mainly is built upon understanding, self-reflection and seeking additional information
* **Stra**: strategic approach measures study organization and time management.
* **Surf**: surface approach comprises motivation and superficial reasons for studying.
* **Points**: points awarded from the exam.

## Overview of the data

A scatterplot of all variables is presented as follows:

```{r}
# Printing the general scatterplot
ggpairs(learning_survey_data, mapping = aes(col = gender, alpha = 0.3), lower = list(combo = wrap("facethist", bins = 20)))

```

The *attitude* variable has significantly higher correlation coefficient with *points* than other variables.

## Regression model fitting

Attitude, strategic learning and surface approach are used as explanatory variables for the exam points outcome.

```{r}
# Creating a linear model
exam_points_model <- lm(points ~ attitude + stra + surf, data = learning_survey_data)
summary(exam_points_model)
```

By adjusting the linear model by removing the least significant variable, a better model might be obtained.
The variable to be removed in this case will be *surf*.

```{r}
# Adjusting the linear model slightly
exam_points_model <- lm(points ~ attitude + stra, data = learning_survey_data)
```

## Model summary

```{r}
summary(exam_points_model)
```

The R squared value tells that the variables explain 21% of the response variable *points*.

## Model validation

```{r}
# ggplot(learning_survey_data, aes(x = stra, y = surf, col = gender))

par(mfrow = c(2,2))
plot(exam_points_model, which = c(1,2,5))

```
