# Exercise 3

The created data (*alc.csv*) is read into a variable and necessary libraries are loaded (*ggplot2* and *GGally* for creating plots).
The data creation script can be found [here](https://github.com/CGBoing/IODS-project/blob/master/data/create_alc.R).

```{r}
library(ggplot2)
library(GGally)
library(dplyr)
alc_survey_data <- read.csv("./data/alc.csv", header = TRUE)
```

## Description of the data

[Data information](https://archive.ics.uci.edu/ml/datasets/Student+Performance)

## Possible factors related to alcohol consumption

Let's select 4 variables that might be related to alcohol consumption:

|Variable|Short name|Justification/hypothesis|
|--------|----------|------------------------|
|Nursery school attendance|*nursery*|higher activity|
|Extra-curricular activities|*activities*||
||||
|In a romantic relationship|*romantic*|being in a romantic relationship could be __|

## Testing the hypothesis



```{r}
logistic_model <- glm(high_use ~ failures + absences + sex, data = alc_survey_data, family = "binomial")
summary(logistic_model)
coef(logistic_model)
odds_ratios <- coef(logistic_model) %>% exp
confidence_intervals <- confint(logistic_model) %>% exp
cbind(odds_ratios, confidence_intervals) # print
```